Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-11 delegations.tex
Modify definition of verifiability

\begin{definition}
	A quantum delegation protocol is \emph{$\delta,\epsilon$-verifiable} if the verifier's output distribution is within $\delta$ of the true distribution whenever it interacts with a prover whose probability to be accepted is greater than $\epsilon$.
\end{definition}

>>>>

\begin{definition}
	A quantum delegation protocol is \emph{$\delta(\epsilon)$-verifiable} if the verifier's output distribution is within $\epsilon$ of the true distribution whenever it interacts with a prover whose probability to be accepted is greater than $\delta$.
\end{definition}
